A Survey on Ordered Binary Decision Diagrams

### 2015-09-14 paper.tex
Add unique-table integration to graph representation
Start dynamic variable ordering

Implementing complement edges enables one to compute the complement and identify
complement functions in constant time (because $f$ and $\overline{f}$ use the same
node). According to Brace et al.~\cite{BRACE90} this reduces the total runtime
to form the OBBDD by almost a factor of 2 (for 12 examples). \tbr

@@

\begin{figure}[ht]
    \centering
    \includestandalone[height = 3cm]{figs/min-obdd}
    \label{fig:min-obdd}
    \caption{Minimized OBDD (optimal).}
\end{figure}
\tbd

>>>>

Implementing complement edges enables one to compute the complement and identify
complement functions in constant time (because $f$ and $\overline{f}$ use the same
node). According to Brace et al.~\cite{BRACE90} this reduces the total runtime
to form the OBBDD by almost a factor of 2 (for 12 examples).

Another refinement to the graph representation, also proposed by Brace et
al.~\cite{BRACE90}, is to integrate the unique-table into the graph representation,
i.e. linking the collision chain of each node to the corresponding unique-table
entry, to improve memory usage. \tbr

@@

For an OBDD package it is desirable to provide the possibility to automatically 
choose a good, though not optimal variable order for arbitrary functions. Of
course, there exist heuristics to order variables before processing but
Rudell~\cite{RUDELL93} proposed to integrate the determination and maintainance
of the variable order into the OBDD package itself. This approach to the variable
ordering problem is called \textit{dynamic variable ordering} and removes the
necessity of choosing a variable ordering beforehand.

Dynamic variable ordering executes the \textit{sifting} algorithm, also proposed
by Rudell~\cite{RUDELL93}, to reorder the variables periodically and so minimize
the size of the OBDD.

\begin{figure}[ht]
    \centering
    \includestandalone[height = 3cm]{figs/min-obdd}
    \label{fig:min-obdd}
    \caption{Minimized OBDD (optimal).}
\end{figure}
\tbr
